### 2016-11-28 paper/paper.tex
more on VAE (introduction)

%----------------------------------
% Variational Autoencoders
%----------------------------------
\section{Variational Autoencoders}
\label{sec:vae}

>>>>

%----------------------------------
% Variational Autoencoders
%----------------------------------
\section{Variational Autoencoders}
\label{sec:vae}
Variational Autoencoders (VAE) have been introduced in 2014 by Kingma and Welling which uses variational inference to perform efficient inference and learning in deep latent models.
To define VAEs, we first declare the observed variables $x$, as well as latent variables $z$.
VAEs are directed graphical models where we wish to infer \emph{good} low-dimensional latent variables from the input data.
In this setup we define $p(x,z)$ as the joint probability distribution over both input and latent variables.
Performing statistical inference means computing $p(z|x)$ which is intractable in all but very simple cases (integrating over it, show calc).

In this setup we have observed variables $x$ from which we would like to infer latent variables $z$
